---
title: "Exercise 8"
author: "0316213 Yu-Wen Pu"
date: "2018-05-13"
output:
  pdf_document:
    includes:
      in_header: ../week03b/header.tex
    latex_engine: xelatex
---

```{r}
knitr::opts_chunk$set(results = "hold")#, fig.retina = 2)
set.seed(1830)
```

##### 19.11

```{r}
x <- matrix(c(22, 187, 19, 74), byrow = TRUE, ncol = 2)
chisq.test(x, correct = FALSE)
```

Yes. **ADD classification** and **remedial/nonremedial English enrollment** are not independent. ($\alpha=0.05$)

##### 19.12

a) See below.

```{r}
(x <- matrix(c(22, 187, 2, 17, 1, 11, 3, 16,
               2, 9, 4, 7, 3, 8, 4, 6),
             byrow = TRUE, ncol = 2))
```

```{r}
(result <- chisq.test(x, correct = FALSE))
```

b) **Exhibition of ADD-like behaviors** and **remedial/nonremedial English enrollment** are not independent. ($\alpha=0.05$)

c) See below.

Expected frequencies:

```{r}
result$expected
```

If the expected frequency is small, the observed frequency cannot be normally distributed around it. Thus the chi-square test may be invalid.

Solution: Use Fisher's Exact Test.

```{r}
fisher.test(x)
```

Got the same conclusion. ($\alpha=0.05$)

##### 19.13

結果是隨機的，各類別平分 N (sample size, = 41)。**19.12** 的假設是 **Exhibition of ADD-like behaviors** 與 **remedial/nonremedial English enrollment** 彼此獨立。

##### 9.1

```{r}
d <- read.table("SubSaharanInfMort.dat", header = TRUE, sep = "",
                na.strings = "NA", fileEncoding = "ISO-8859-1")
head(d)
```

```{r}
library(ggplot2)
ggplot(d, aes(x = income, y = infmort)) +
    geom_point() +
    geom_smooth(method = "lm", color = "red", se = FALSE) +
    labs(x = "per capita income (in U.S. dollars)", y = "infant mortality")
```

effect of outliers: 使負相關更明顯，$r^2$ 更大。

##### 9.2

```{r}
rownames(d) <- d$country
d$country <- NULL
d[is.na(d)] <- 0  # replace NA with 0
head(d)
```

```{r}
cor(d)
```

##### 9.4

```{r}
cor(d$infmort, d[, names(d) != "infmort"]) ** 2
```

Per capita income.

##### 9.5

嬰兒死亡率與人均收入成負相關，人均收入愈高，嬰兒死亡率愈低；嬰兒死亡率也與避孕措施的使用率成負相關，避孕措施的使用率愈高，嬰兒死亡率愈低。

##### 9.6

```{r}
summary(d)
```

在撒哈拉以南非洲（Sub-Saharan Africa），相較於年幼產婦的比例（中位數達 $21\%$），高齡產婦的比例不高（中位數僅 $5\%$），因此並非主要的風險來源；但在其他地區，相較於年幼產婦的比例，高齡產婦的比例偏高，因此會是一個風險因子。

##### 9.7



##### 9.8


